Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-16 Article.tex
Correction of bad label position in section names

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Materials and experiments\label{sec:MaterialsExperiments}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsection{Experimental procedure and compression tests results\label{subsec:ExperimentalProcedure}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsection{DRX model's parameters identification\label{subsec:DRXParameters}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{ANN based filtering model's architecture\label{subsec:ANNbasics}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{ANN filtering based model's application \label{subsec:ANNapplication}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{Critical conditions evaluation\label{subsec:CrConditions}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsection{DRXmodel parameters evaluation\label{subsec:DRXparams}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Numerical simulation of the compression\label{sec:NumSim}}
%----------------------------------------------------------------------------------
In this section, we will focus on numerically validating the previously performed identification of dynamic recrystallization.
This requires establishing a constitutive law capable of accurately predicting the material's plastic deformation.
In our previous publication (Tize Mha \eal \cite{TizeMha-2023}), we conducted a comparison between analytical constitutive laws and a neural network-based approach.
The results revealed an artificial neural network model as the most appropriate option for this material.
As a result, this section has two main focuses: first, a summary of the ANN-based constitutive law identification, as previously presented; and second, the incorporation of this identified ANN model with the JMAK model to predict dynamic recrystallization behavior.

%----------------------------------------------------------------------------------
\subsection{Identification of the ANN constitutive law\label{subsec:ANNConstitutiveLaw}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsection{Dynamic recrystallization simulation\label{subsec:DRXSimulation}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{Temperature and strain rate effects \label{subsec:TempSReffect}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{Comparison with some experiments\label{subsec:ExpValid}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Conclusions\label{sec:Conclusions}}
%----------------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}\label{sec:Appendix}

>>>>

%----------------------------------------------------------------------------------
\section{Introduction}\label{sec:Introduction}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Materials and experiments}\label{sec:MaterialsExperiments}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsection{Experimental procedure and compression tests results}\label{subsec:ExperimentalProcedure}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsection{DRX model's parameters identification}\label{subsec:DRXParameters}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{ANN based filtering model's architecture}\label{subsec:ANNbasics}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{ANN filtering based model's application} \label{subsec:ANNapplication}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{Critical conditions evaluation}\label{subsec:CrConditions}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsection{DRXmodel parameters evaluation}\label{subsec:DRXparams}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Numerical simulation of the compression}\label{sec:NumSim}
%----------------------------------------------------------------------------------
In this section, we will focus on numerically validating the previously performed identification of dynamic recrystallization.
This requires establishing a constitutive law capable of accurately predicting the material's plastic deformation.
In our previous publication (Tize Mha \eal \cite{TizeMha-2023}), we conducted a comparison between analytical constitutive laws and a neural network-based approach.
The results revealed an artificial neural network model as the most appropriate option for this material.
As a result, this section has two main focuses: first, a summary of the ANN-based constitutive law identification, as previously presented; and second, the incorporation of this identified ANN model with the JMAK model to predict dynamic recrystallization behavior.

%----------------------------------------------------------------------------------
\subsection{Identification of the ANN constitutive law}\label{subsec:ANNConstitutiveLaw}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsection{Dynamic recrystallization simulation}\label{subsec:DRXSimulation}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{Temperature and strain rate effects}\label{subsec:TempSReffect}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\subsubsection{Comparison with some experiments}\label{subsec:ExpValid}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Conclusions}\label{sec:Conclusions}
%----------------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
%\appendixstart
%\appendix
%\section[\appendixname~\thesection]{}\label{sec:Appendix}
